QPLIB: A Library of Quadratic Programming Instances

### 2018-08-08 QPLIB-2.2.tex
Update QPLIB-2.2.tex

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  %Note that (\textit{D}) and (\textit{C}) are intended to mean that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    \textcolor{red}{Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}

@@

\textcolor{red}{
Furthermore, as previously remarked, a not (positive or negative) definite $Q^i$ does not necessarily correspond to a nonconvex feasible region. For instance, it is well-known that Second-Order Cone Programs have convex feasible regions; when represented in terms of quadratic constraints, however, they correspond to $Q^i$ with one negative eigenvalue. In our taxonomy we still consider the corresponding instances as \textit{**Q} ones, with no attempt to detect the different special structures that actually correspond to convex feasible regions. Although this may lead to classify as ``potentially nonconvex'' some instances that are in fact convex, our choice is justified by the fact that not all QP solvers are capable of detecting and exploiting these structures, which means that the instance can actually be treated as a nonconvex one even if it is not.\\
}
\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same form as they have been provided to us by the original contributors. The rationale of this choice is that reformulation techniques, like the ones discussed here and others, are typically motivated by the fact that they make the instance easier to solve for one specific class of solvers. This being a bias that we do not want to add we have chosen to keep the instances in their ``natural'' form, this being the one in which the original contributor initially wrote them.
}

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  %Note that (\textit{D}) and (\textit{C}) are intended to mean that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    {Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}

@@

{
Furthermore, as previously remarked, a not (positive or negative) definite $Q^i$ does not necessarily correspond to a nonconvex feasible region. For instance, it is well-known that Second-Order Cone Programs have convex feasible regions; when represented in terms of quadratic constraints, however, they correspond to $Q^i$ with one negative eigenvalue. In our taxonomy we still consider the corresponding instances as \textit{**Q} ones, with no attempt to detect the different special structures that actually correspond to convex feasible regions. Although this may lead to classify as ``potentially nonconvex'' some instances that are in fact convex, our choice is justified by the fact that not all QP solvers are capable of detecting and exploiting these structures, which means that the instance can actually be treated as a nonconvex one even if it is not.\\
}
{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same form as they have been provided to us by the original contributors. The rationale of this choice is that reformulation techniques, like the ones discussed here and others, are typically motivated by the fact that they make the instance easier to solve for one specific class of solvers. This being a bias that we do not want to add we have chosen to keep the instances in their ``natural'' form, this being the one in which the original contributor initially wrote them.
}
